---
title: "preprocessing"
output: html_document
---
python으로 EDA한 글: https://arena.kakao.com/forum/topics/191

******** R studio 새로 열 때마다 아래 chunk 돌려주세용
data file은 최초 한번만 read해주시면 됩니다.

1. Parsing json file as data frame
```{r}
# 작업경로
# Project 폴더
# ㄴ data 폴더
#    ㄴ song_meta.json 
#    ㄴ train.json
#    ㄴ genre_gn_all.json
# ㄴ R or Rmd 파일들
# 위와 같이 저장하고 작업경로 본인 컴퓨터상에서 Project 폴더로 설정해주세요 (코드 통일을 위해서)
# 예시 : setwd("D:/수강과목/DSR/Project")

if (!require("ggplot2")) install.packages("ggplot2")
library(ggplot2)
if (!require("dplyr")) install.packages("dplyr")
library(dplyr)
if (!require("jsonlite")) install.packages("jsonlite")
library(jsonlite)
if (!require("data.table")) install.packages("data.table")
library(data.table)
if (!require("stringr")) install.packages("stringr")
library(stringr)
if (!require("lubridate")) install.packages("lubridate")
library(lubridate)
# 분석하면서 새로 쓰인 package는 아래 공간에 추가해주세요.


# Importing python running package (if needed)
# if (!require("reticulate")) install.packages("reticulate")
# library(reticulate)
```

  1) genre_gn_all.json
```{r}
# 파일 로드할 때 한글 깨짐 방지
Sys.getlocale()
Sys.setlocale("LC_ALL", "C")
df <- fromJSON(readLines("./data/genre_gn_all.json", encoding = "UTF-8"))
Sys.setlocale("LC_ALL", "Korean")

df <- as.data.frame(df, stringsAsFactors = FALSE)
t_df <- t(df)
# View(new_df)
t_df <- as.data.frame(t_df, stringsAsFactors = FALSE)
new_df <- tibble::rownames_to_column(t_df, "gr_code")
names(new_df)[2] <- c("gr_name")
gr_df <- new_df

# 가공하는 데에 사용한 object 삭제, genre code df만 남김
rm("df", "t_df", "new_df")
View(gr_df)
str(gr_df)
```

  2) song_meta.json
```{r}
# Sys.setlocale("LC_ALL", "C")
# df <- fromJSON(readLines("./data/song_meta.json", encoding = "UTF-8"))
# Sys.setlocale("LC_ALL", "Korean")
# df <- as.data.frame(df, stringsAsFactors = FALSE)

song_df <- stream_in(file("./data/song_meta.json"))
class(song_df)
View(song_df)
```
  
  3) train.json
```{r}
playlist_df <- stream_in(file("./data/train.json"))

```

2. Refine the data
 1) genres
 Look up main categories of genre code
```{r}
main_gr <- gr_df$gr_code

# Add main genre code column to gr_df 
main_gr <- paste0(substr(main_gr, 1, 4), "00")
main_gr
gr_df <- gr_df %>% mutate(main_gr_code = main_gr)
View(gr_df)
gr_df <- gr_df[c(3, 1, 2)]

# Make new data frame that contains only main gerne codes and their names 
main_list <- grep("*[0-9][0-9][0][0]", gr_df$gr_code, value = T)
main_gr_name <- gr_df$gr_name[gr_df$gr_code %in% main_list]
main_gr_df <- cbind(data.frame(main_list, stringsAsFactors = FALSE), data.frame(main_gr_name, stringsAsFactors = FALSE))
colnames(main_gr_df) = c("main_gr_code", "main_gr_name")
View(main_gr_df)
str(main_gr_df)

rm("main_list", "main_gr")

# Select all sub(detailed) genres in "랩/힙합" -> 얘처럼 같은 대분류에 다른 소분류가 여러 개 있음
searchByName <- main_gr_df %>% filter(main_gr_name == "랩/힙합")
gr_df %>% filter(gr_df$main_gr_code %in% searchByName$main_gr_code)

# (Optional) The Same search function with user input
userInput <- readline("Enter main genre: ")
searchByName <- main_gr_df %>% filter(main_gr_name == userInput)
gr_df %>% filter(gr_df$main_gr_code %in% searchByName$main_gr_code)

# Which high genre has the most sub(detailed) genres? -> main gr각각을 unique한 것으로 생각하고 조회한 것
sub_gr_count <- gr_df %>% group_by(main_gr_code) %>% summarise(numOfGenres = n()) %>% mutate(main_gr_name = main_gr_df$main_gr_name)
sub_gr_count <- sub_gr_count[c(1, 3, 2)]
sub_gr_count
sub_gr_count %>% filter(numOfGenres == max(numOfGenres))
# Its sub genres
mostSub <- sub_gr_count %>% filter(numOfGenres == max(numOfGenres)) %>% select(main_gr_name)
mostSub
searchByName <- main_gr_df %>% filter(main_gr_name == mostSub$main_gr_name)
gr_df %>% filter(gr_df$main_gr_code %in% searchByName$main_gr_code)

# Show bar plots -> 여기서는 main gr를 name으로 조회해서 sub gr가 합산되어 나옴
sub_gr_count %>% ggplot(aes(x = main_gr_name, y = numOfGenres)) +
  geom_bar(stat = "identity", fill = "#009A3E") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Main genres") +
  ylab("Number of sub genres")

```
Comments:
1. There are 254 rows of sub genre codes and 30 rows of main categories in genre codes. Main genres have forms of GN--00.
2. There are multiple main genres with difference codes such as "랩/힙합", "R&B/Soul", etc.
3. Unique main genre with the most sub genres is "어린이/태교." (17 sub genres)
4. In bar plot, we looked up by genre names so that the main genre w/ the most subs is 록/메탈.

 2) Songs
 
```{r}
# issue_date column - Convert character to date type
# song_meta는 새로 읽는 게 오래걸려서 새 df에 옮겨놓고 사용합니다.
sg_df <- song_df

sg_df$issue_date <- ymd(sg_df$issue_date)   # 21620개의 NA & 2022년 issue도 있음ㅋㅋ
head(sg_df)
# What is the time period of issue dates?
range(sg_df$issue_date, na.rm = TRUE)
# How many songs in each year?
year_cnt <- sg_df %>% group_by(year(issue_date)) %>% summarise(song_cnt = n())
na.omit(year_cnt)
colnames(year_cnt) = c("year", "song_cnt")
year_cnt
year_cnt %>% ggplot(aes(x = year, y = song_cnt)) +
  geom_bar(stat = "identity", fill = "#7CB4FD") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Year") +
  ylab("Number of songs") +
  ggtitle("Number of songs in each year")

# Zoom in to 1975-2020
year_cnt %>% ggplot(aes(x = year, y = song_cnt)) +
  geom_bar(stat = "identity", fill = "#7CB4FD") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Year") +
  ylab("Number of songs") +
  ggtitle("Number of songs in each year")
```
Comments:
1. There are 21620 NAs in issue_date column.
2. Time period of issue date of songs is from "1900-01-01" to "2022-01-13."


 3) Playlists
```{r}

```
 
3. EDA
 3) Make word cloud with hashtags

